### 2018-08-28 paper/finitecomplete-failures.tex
Added complexity considerations

>>>>

% ==========================================================================
\subsection{Complexity Considerations}
\label{sec:complexity}

As can be seen from the specification of the test cases $U_F(k)$, the number of 
executions ending in a $\epass$-event corresponds to the number $\ell$ of traces $s$ 
of $P$ with length less or equal $p$, multiplied by the number $h$ of minimal hitting sets in
$\minhits(P/s)$. The first factor 
has worst-case upper bound $\ell\le |\Sigma|^p$.
Given a set $\minaccs(P/s) = \{ A_1,\dots, A_a \}$ of   minimal acceptances,
the cardinality $h$ of $\minhits(P/s)$ is maximal for the case where all $A_i$ are disjoint.
In this case,  $h=|\minhits(P/s)| = \prod_{i=1}^a|A_i|$. This yields a worst-case upper bound $h\le 2^{\frac{|\Sigma|}{2}}$. This is better than the upper bound $(2^{|\Sigma|}-1)$
resulting from the tests suggested in~\cite{Hennessy:1988:ATP:50497}, where {\it every}
non-empty 
subset of $\Sigma$ whose events cannot be completely refused in a given process state
has to be checked during test executions. This improvement becomes more significant for process states where the number of minimal acceptances is small. In the best case, where
 $\minaccs(P/s) = \{ A_1  \}$, we just have $|A_1|$ minimal hitting sets (each consisting of a single element) to test, while the tests from~\cite{Hennessy:1988:ATP:50497} 
 require $(2^{|A_1|}-1)$ sets to be checked. From Lemma~\ref{lemma:hseta} we know that 
 the worst-case bound $h\le 2^{\frac{|\Sigma|}{2}}$ cannot be further improved, since 
the full collection of minimal hitting sets needs to be checked in order to verify
the $conf$ relation.

Summarising, the number of executions involved in one adaptive test $U_F(k)$ is bounded
by $|\Sigma|^k\cdot 2^{\frac{|\Sigma|}{2}}$. According to Theorem~\ref{th:failurestest},
we need to execute these test for $k = 0,\dots,pq$; this results in a worst-case bound
of (we use the formula for the sum of the geometric progression here)
\[
    2^{\frac{|\Sigma|}{2}}\cdot\big( \frac{1-|\Sigma|^{pq}}{1-|\Sigma|} \big),
    \quad\text{or, asymptotically,}\quad O(2^{(\frac{|\Sigma|}{2} + pq)}).
\]

It is discussed in Section~\ref{sec:conc} that the term $pq$ occurring in this bound can be significantly reduced by using more complex test cases that need not execute {\it all} 
traces of $P$ with length less or equal to $pq$.
